### 2022-06-16 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@e964b8d8ff0c2847e33b1bf3933454c77c226731 🚀

Nevertheless, locally diverse and virus-rich bat communities could
represent an increased risk of spillover under climate change through
the creation of novel interactions (\textbf{Ice ice berg berg}), and
therefore the diversity of betacoronavirus strains should similarly be
ccounted for. In fig.~\ref{fig:richness} (bottom), we contrast the
evolutionary distinctiveness of bats and viruses -- this reveals a
slightly different portrait than bat richness alone. Chiropterans can be
classified, from a macro-evolutionary standpoint, as microchiroptera and
macrochiroptera, where macrochiroptera have an older history from an
evolutionary perspective compared to macrochiroptera (Teeling et al.
2005, Springer 2013). Specifically, we would expect that the so-called
``New World'' group of bats, being more evolutionary distinct, would
also have evolutionary distinct viruses. Indeed fig.~\ref{fig:richness}
(bottom) reveals it to be the case, and this region harbors a distinct
bat-betacoronavirus complex. By contrast, South-Eastern Asia has a lot
of non-evolutionary distinct bats, but evolutionary-distinct viruses.

@@

>>>>

Nevertheless, locally diverse and virus-rich bat communities could
represent an increased risk of spillover under climate change through
the creation of novel interactions (Carlson et al. 2022), and therefore
the diversity of betacoronavirus strains should similarly be ccounted
for. In fig.~\ref{fig:richness} (bottom), we contrast the evolutionary
distinctiveness of bats and viruses -- this reveals a slightly different
portrait than bat richness alone. Chiropterans can be classified, from a
macro-evolutionary standpoint, as microchiroptera and macrochiroptera,
where macrochiroptera have an older history from an evolutionary
perspective compared to macrochiroptera (Teeling et al. 2005, Springer
2013). Specifically, we would expect that the so-called ``New World''
group of bats, being more evolutionary distinct, would also have
evolutionary distinct viruses. Indeed fig.~\ref{fig:richness} (bottom)
reveals it to be the case, and this region harbors a distinct
bat-betacoronavirus complex. By contrast, South-Eastern Asia has a lot
of non-evolutionary distinct bats, but evolutionary-distinct viruses.

@@

\leavevmode\hypertarget{ref-Carlson2022CliCha}{}%
Carlson, C. J. et al. 2022. Climate change increases cross-species viral
transmission risk. - Nature: 1--1.
